### 2009-03-18 doc/storage_system/arc-storage-manual.tex
starting an administrator's and user's manual

\begin{verbatim}
http://svn.nordugrid.org/
svn co http://svn.nordugrid.org/repos/nordugrid/arc1/trunk arc1   
README file for dependencies
$ ./autogen.sh
$ ./configure --disable-java --disable-a-rex-service --disable-isi-service --disable-charon-service --disable-compiler-service --disable-paul-service --disable-sched-service
--prefix

@@

RLS:                yes
GridFTP:            yes
LFC:                no
RSL:                yes
SAML:               yes
MYSQL CLIENT LIB:   no
gSOAP:              no

Included components:
A-Rex service:      no
ISI service:        no
CHARON service:     no
HOPI service:       yes
SCHED service:      no
STORAGE service:    yes
PAUL service:       no
SRM client (DMC):   no
GSI channel (MCC):  yes

$ make

$ sudo make install

@@

>>>>

In this section we will follow the installation of the ARC storage system on a freshly installed debian linux machine.

Get the latest ARC code from the subversion (\verb!http://svn.nordugrid.org/!):

\begin{verbatim}
$ svn co http://svn.nordugrid.org/repos/nordugrid/arc1/trunk arc1
\end{verbatim}

Let's check the README file for all the dependencies, and install them:

\begin{verbatim}
$ sudo aptitude install build-essential
$ sudo aptitude install autoconf
$ sudo aptitude install gettext
$ sudo aptitude install cvs
$ sudo aptitude install libtool
$ sudo aptitude install pkg-config
$ sudo aptitude install libglibmm-2.4-dev
$ sudo aptitude install python-dev
$ sudo aptitude install swig
$ sudo aptitude install libxml2-dev
$ sudo aptitude install libssl-dev
\end{verbatim}

Run the \verb!autogen! and \verb!configure! scripts (you may want to specify target directories for the installation with the \verb!--prefix! option):

\begin{verbatim}
$ cd arc1
$ ./autogen.sh
$ ./configure --disable-java --disable-a-rex-service --disable-isi-service --disable-charon-service --disable-compiler-service --disable-paul-service --disable-sched-service
--prefix

@@

RLS:                no
GridFTP:            no
LFC:                no
RSL:                no
SAML:               no
MYSQL CLIENT LIB:   no
gSOAP:              no

Included components:
A-Rex service:      no
ISI service:        no
CHARON service:     no
HOPI service:       yes
SCHED service:      no
STORAGE service:    yes
PAUL service:       no
SRM client (DMC):   no
GSI channel (MCC):  no

@@

We can start to compile it:

\begin{verbatim}
$ make
\end{verbatim}

And then install it (you need to be root if you want to install it to the default location):

\begin{verbatim}
$ sudo make install
\end{verbatim}

Maybe we should run \verb!ldconfig! to refresh the list of libraries:

\begin{verbatim}
$ ldconfig
\end{verbatim}

We can check if the python packages are installed correctly:

\begin{verbatim}
$ python
Python 2.5.2 (r252:60911, Jan  4 2009, 17:40:26) 
[GCC 4.3.2] on linux2
Type "help", "copyright", "credits" or "license" for more information.
>>> import arc
>>> import storage
>>> import arcom
>>> 
\end{verbatim}

If there is no error on importing any of the packages, we are good to go.
